\mytitle{}

### 2019-07-24 paper/infocom.tex
Starting arch plot...
Diagram done.

\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, calc, fit, positioning}

@@

?? Here is where I would put my ramblings about system architecture...

>>>>

\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{varwidth}
\usetikzlibrary{arrows.meta, calc, fit, positioning, shapes.misc}

@@

%?? Here is where I would put my ramblings about system architecture...
We present a description...

\subsection{Stats API}
?? API between agent and switches/other agents? Push/Pull API on stats? How do they share experience? Could broadcasts aid both?

?? How do stats get from switcehs to the agent?

?? What does experience transfer look like? Why?

\begin{figure}
	\centering
	\resizebox{\linewidth}{!}{\begin{tikzpicture}
		\node(remote){Remote};

		%%%

		\node[below=0.2 of remote](swpos){};
		\node[fill=white!80!uofgcobalt, draw=black, minimum height=1.5cm, minimum width=2cm, below right= 0.1 of swpos.north west](sw1){};
		\node[fill=white!80!uofgcobalt, draw=black, minimum height=1.5cm, minimum width=2cm, below right= 0.1 of sw1.north west](sw2){};
		\node[fill=white!80!uofgcobalt, draw=black, minimum height=1.5cm, minimum width=2cm, below right= 0.1 of sw2.north west](switch){};
		\node[below right, inner sep=2pt] at (switch.north west) {\small Switch};
		\node[fill=white!90!uofgcobalt, draw, rectangle, rounded corners=0.05cm, above=0.1] (oswlc) at (switch.south) {\begin{varwidth}{1.5 cm}\small \centering Load\\Collector\end{varwidth}};

		%

		\node[right=2 of swpos](epos){};
		\node[fill=white!80!uofgthistle, draw=black, minimum height=1.5cm, minimum width=3.5cm, below right= 0.1 of epos.north west](e1){};
		\node[fill=white!80!uofgthistle, draw=black, minimum height=1.5cm, minimum width=3.5cm, below right= 0.1 of e1.north west](e2){};
		\node[fill=white!80!uofgthistle, draw=black, minimum height=1.5cm, minimum width=3.5cm, below right= 0.1 of e2.north west](egress){};
		\node[below right, inner sep=2pt] at (egress.north west) {\small Egress Switch};
		\node[fill=white!90!uofgthistle, draw, rectangle, rounded corners=0.05cm, above=0.1] (eglc) at ($(egress.south) + (-0.85,0)$) {\begin{varwidth}{1.5 cm}\small \centering Load\\Collector\end{varwidth}};
		\node[fill=white!90!uofgthistle, draw, rectangle, rounded corners=0.05cm, right=0.1] (egest) at (eglc.east) {\begin{varwidth}{1.5 cm}\small \centering Estimator\\$g(\cdot)$\end{varwidth}};

		%

		\node[right=3.5 of epos](apos){};
		\node[fill=white!60!uofgpumpkin, draw=black, minimum height=1.5cm, minimum width=2cm, below right= 0.1 of apos.north west](a1){};
		\node[fill=white!60!uofgpumpkin, draw=black, minimum height=1.5cm, minimum width=2cm, below right= 0.1 of a1.north west](a2){};
		\node[fill=white!60!uofgpumpkin, draw=black, minimum height=1.5cm, minimum width=2cm, below right= 0.1 of a2.north west](otheragent){};
		\node[below right, inner sep=2pt] at (otheragent.north west) {\small Agent VF};
		\node[fill=white!90!uofgpumpkin, draw, rectangle, rounded corners=0.05cm, above=0.3] (oasa) at (otheragent.south) {\begin{varwidth}{1.5 cm}\small \centering Stats API\end{varwidth}};

		%

		\node[below=2.5 of remote.west](linestart){};
		\path let \p1 = (linestart) in node (lineend) at (9,\y1){};
		\draw [dashed] (linestart) -- (lineend);

		%%%

		\node[below=2.6 of remote](local){Local};

		%%%

		\node[below=0.2 of local](aswpos){};
		\node[fill=white!80!uofgthistle, draw=black, minimum height=3.5cm, minimum width=2.2cm, below right= 0.1 of aswpos.north west](aswitch){};
		\node[below right, inner sep=2pt] at (aswitch.north west) {\small Agent Switch};
		\node[fill=white!90!uofgthistle, draw, rectangle, rounded corners=0.05cm, above=0.1] (aswoft) at (aswitch.south) {\begin{varwidth}{1.5 cm}\small \centering OpenFlow\\Tables\end{varwidth}};
		\node[fill=white!90!uofgthistle, draw, rectangle, rounded corners=0.05cm, above=0.1] (aswsc) at (aswoft.north) {\begin{varwidth}{1.5 cm}\small \centering Stats\\Collector\end{varwidth}};
		\node[fill=white!90!uofgthistle, draw, rectangle, rounded corners=0.05cm, above=0.1] (aswlc) at (aswsc.north) {\begin{varwidth}{1.5 cm}\small \centering Load\\Collector\end{varwidth}};

		%

		\node[right=3 of aswpos](avfpos){};
		\node[fill=white!60!uofgpumpkin, draw=black, minimum height=3.5cm, minimum width=4.5cm, below right= 0.1 of avfpos.north west](avf){};
		\node[below right, inner sep=2pt] at (avf.north west) {\small Agent VF};
		\node[fill=white!90!uofgpumpkin, draw, rectangle, rounded corners=0.05cm, below=0.15] (avfsa) at ($(avf.north) + (0.2,0)$) {\begin{varwidth}{1.5 cm}\small \centering Stats API\end{varwidth}};
		\node[fill=white!90!uofgpumpkin, draw, rectangle, rounded corners=0.05cm, below=0.9] (avfdb) at (avfsa.south west) {\begin{varwidth}{1.5 cm}\small \centering Flowstate\\Database\end{varwidth}};
		\node[fill=white!90!uofgpumpkin, draw, rectangle, rounded corners=0.05cm, right=0.1] (avfsched) at (avfdb.east) {\begin{varwidth}{1.5 cm}\small \centering TRSE\\Scheduler\end{varwidth}};
		\node[fill=white!90!uofgpumpkin, draw, rectangle, rounded corners=0.05cm, below=2.3] (avfcore) at (avfsa.south) {\begin{varwidth}{1.5 cm}\small \centering Core\end{varwidth}};
		\node[fill=white!90!uofgpumpkin, draw, rectangle, rounded corners=0.05cm, right=0.8] (avfrl) at (avfcore.east) {\begin{varwidth}{1.5 cm}\small \centering RL\end{varwidth}};

		%%%

		\tikzset{>=stealth}

		\draw[thick, ->] (aswlc) -- (avfsa.west) node[midway,above] {\tiny Current load};
		\draw[thick, ->] (aswsc) -- (avfsa.west) node[midway,sloped, above] {\tiny Flow stats};

		\draw[thick, ->] (oswlc) -- (avfsa) node[midway,above, sloped] {\tiny Current load};

		\draw[thick, ->] (eglc) -- (avfsa) node[midway,above, sloped] {\tiny Current load};
		\draw[thick, ->] (egest) -- (avfsa) node[midway,above, sloped] {\tiny Estimation data};

		\draw[thick, <->] (oasa) -- (avfsa) node[midway,above, sloped] {\tiny Experience};

		\draw[thick, ->] (avfsa) -- (avfdb) node[midway,above, sloped] {\tiny State};
		\draw[thick, ->] (avfsa) -- (avfsched) node[midway,above, sloped] {\tiny Live flows};

		\draw[thick, ->] (avfcore) -- (aswoft) node[midway,above, sloped] {\tiny Packet drop rules};
		\draw[thick, <->] (avfcore) -- (avfdb) node[midway,below, sloped] {\tiny State};
		\draw[thick, <->] (avfcore) -- (avfsched) node[midway,below, sloped] {\tiny Work};
		\draw[thick, <-] ($(avfcore.east) + (0,0.1)$) -- ($(avfrl.west) + (0,0.1)$) node[midway,above, sloped] {\tiny Actions};
		\draw[thick, ->] (avfcore) -- (avfrl) node[midway,below, sloped] {\tiny State};

		\draw[thick, ->] (avfsa.east) to [out=0, in=45] (avfrl.north);
		\node[right=0.3] at (avfsa.east) {\tiny Experience};
	\end{tikzpicture}}
	\caption{System architecture  for our RL-driven DDoS defence system.}
\end{figure}
